### 2019-04-01 README.Rmd
Fix some typos

You can map estimated gust winds, rather than sustained winds (the default), using the argument `wind_var = "vmax_gust"`. Further, we have included a second source of estimated winds in the data available in `hurricaneexposuredata`. These wind estimates are based on the wind radii in the Extended Best Tracks dataset (you can find out more about this data in the helpfile for the `ext_tracks_wind` dataset). These data provide estimates of which counties were exposured during a storm to sustained winds in four categories: 0--34 knots; 34--50 knots;  50--64 knots; and 64 knots or higher. Therefore, these data provide a categorical rather than continuous estimate of county wind speeds. However, they may be preferable to the model wind speeds for some storms, especially storms in extra-tropical transition. Further, you may find it interesting to use these data in a sensitivity analysis, to compare if impact study results are sensitive to whether these wind data or the modeled wind data are used for exposure classification. You can create a wind map based on this data using the `wind_source = "ext_tracks"` argument in the `map_counties` function. For example, to map estimated winds during Hurricane Katrina based on the Extended Best Tracks wind radii, you can run:

>>>>

You can map estimated gust winds, rather than sustained winds (the default), using the argument `wind_var = "vmax_gust"`. Further, we have included a second source of estimated winds in the data available in `hurricaneexposuredata`. These wind estimates are based on the wind radii in the Extended Best Tracks dataset (you can find out more about this data in the helpfile for the `ext_tracks_wind` dataset). These data provide estimates of which counties were exposed during a storm to sustained winds in four categories: 0--34 knots; 34--50 knots;  50--64 knots; and 64 knots or higher. Therefore, these data provide a categorical rather than continuous estimate of county wind speeds. However, they may be preferable to the model wind speeds for some storms, especially storms in extra-tropical transition. Further, you may find it interesting to use these data in a sensitivity analysis, to compare if impact study results are sensitive to whether these wind data or the modeled wind data are used for exposure classification. You can create a wind map based on this data using the `wind_source = "ext_tracks"` argument in the `map_counties` function. For example, to map estimated winds during Hurricane Katrina based on the Extended Best Tracks wind radii, you can run:
